I don't know, are you sure we want to do this?\\ Sea level adaptation decisions under uncertainty

### 2016-11-20 submission/paper.tex
Minor fixes.

\begin{abstract}
...
\end{abstract}

@@

Section \ref{sealevelproj} describes our approach to projecting sea level. In section \ref{decision_tools} we describe the type of decision problem that we are going to attack. We apply these tools to a sea level projection for Bergen, Norway, %and for Esbjerg, Denmark 
in section \ref{cases}.  In the final section \ref{unc}  we demonstrate the consequences of ignoring the uncertainty in the projections.

@@

\[H_t^{loc,i} + \gamma (t -2000 ) = {\hat b} H_t^{gl,i}  + {\varepsilon _t}\]
where $\gamma$ ie the annual land rise rate, t and $ {\hat b} $ is the regression coefficient relating global to local sea level.

@@

\begin{figure}[!hbpt]
\begin{center}
\includegraphics[width=\linewidth]{AccumulatedFutureLoss.png}
\caption{Distribution of log  accumulated future loss 2016-2100 under RCP 8.5 and assuming that no adaptation measures are implemented.} 
\label{fig:NoAction}
\end{center}
\end{figure}

@@

In many cases sea level rise projections are given as a single number for each scenario, usually the mean or median of the ensemble of projections from different climate models (e.g. \citet{climateimpactgroup}). Sometimes the spread of the ensemble is used to assess the uncertainty in the projections (e.g., the Norwegian Environmental Agency recommends using the upper ensemble value for RCP 8.5 as the basis for planning decision, pers. comm. from Even Nilsson, Norwegian Mapping Authority). In our analysiis there are two more sources of uncertainty, namely the two regression models. Figure \ref{fig:unc} shows the single number (vertical black line), the ensemble spread (histogram), the uncertainty including the global model (red) and the full uncertainty (blue) for Bergen projections of sea level rise relative to 1999 under RCP 8.5. We see that the ensemble range is about 16 cm, whereas the overall uncertainty range is about 40 cm.

\begin{figure}[!hbpt]
\begin{center}
\includegraphics[width=\linewidth]{unc.pdf}
\caption{2050 Bergen sea level projections with uncertainty due to different sources for RCP 8.5. The black line is the median projection (with no uncertainty), while the grey histogram corresponds to the spread of the climate models, the red curve adds the uncertainty due to the relation between global temperature and global sea level, and the blue line that due to downscaling global sea level to Bergen. } 
\label{fig:unc}
\end{center}
\end{figure}

%  ACKNOWLEDGMENTS
\begin{acknowledgments}
This work was funded by NordForsk through project number 74456 ``Statistical Analysis of Climate Projections'' (eSACP) and The Research Council of Norway through project number 243953 ``Physical and Statistical Analysis of Climate Extremes in Large Datasets'' (ClimateXL). The source code for the analysis is implemented in the statistical programming language {\tt R} (\url{http://www.R-project.org}) and is available on GitHub at \url{http://github.com/eSACP/...}.
\end{acknowledgments}

>>>>

\begin{abstract}
Sea level rise has serious consequences for harbor infrastructure, storm drains and sewer systems, and many other issues. Adapting to sea level rise requires comparing different possible adaptation strategies, comparing the cost of different actions (including no action), and assessing at what point in time the chosen strategy should be implemented. All these decisions must be made under considerable uncertainty--in the amount of sea level rise, in the cost of adaptation actions, in the cost of no action. We develop two illustrative examples: for Bergen on Norway's west coast and for Esbjerg on the west coast of Denmark. Different components of uncertainty are visualized. {\color{blue} Findings go here}
\end{abstract}

@@

Section \ref{sealevelproj} describes our approach to projecting sea level. In section \ref{decision_tools} we describe the type of decision problem that we are going to attack. We apply these tools to  sea level projections for Bergen, Norway, and for Esbjerg, Denmark 
in section \ref{cases}.  In the final section \ref{unc}  we demonstrate the consequences of ignoring the uncertainty in the projections.

@@

\[H_t^{loc,i} + \gamma (t -2000 ) = {\hat b} H_t^{gl,i}  + {\varepsilon _t}\]
where $\gamma$ is the annual land rise rate, $t$ denotes year, and $ {\hat b} $ is the regression coefficient relating global to local sea level.

@@

\begin{figure}[!hbpt]
\begin{center}
\includegraphics[width=0.5\linewidth]{AccumulatedFutureLoss.png}
\caption{Distribution of log  accumulated future loss 2016-2100 under RCP 8.5 and assuming that no adaptation measures are implemented.} 
\label{fig:NoAction}
\end{center}
\end{figure}

@@

In many cases sea level rise projections are given as a single number for each scenario, usually the mean or median of the ensemble of projections from different climate models (e.g. \citet{climateimpactgroup}). Sometimes the spread of the ensemble is used to assess the uncertainty in the projections (e.g., the Norwegian Environmental Agency recommends using the upper ensemble value for RCP 8.5 as the basis for planning decision, pers. comm. from Even Nilsson, Norwegian Mapping Authority). In our analysiis there are two more sources of uncertainty, namely the two regression models. Figure \ref{fig:unc} shows the single number (vertical black line), the ensemble spread (histogram), the uncertainty including only the global model (red) and the full uncertainty (blue) for Bergen projections of sea level rise relative to 1999 under RCP 8.5. We see that the ensemble range is about 16 cm, whereas the overall uncertainty range is about 40 cm.

\begin{figure}[!hbpt]
\begin{center}
\includegraphics[width=0.5\linewidth]{unc.pdf}
\caption{2050 Bergen sea level projections with uncertainty due to different sources for RCP 8.5. The black line is the median projection (with no uncertainty), while the grey histogram corresponds to the spread of the climate models, the red curve adds the uncertainty due to the relation between global temperature and global sea level, and the blue line that due to downscaling global sea level to Bergen. } 
\label{fig:unc}
\end{center}
\end{figure}

%  ACKNOWLEDGMENTS
\begin{acknowledgments}
This work was funded by NordForsk through project number 74456 ``Statistical Analysis of Climate Projections'' (eSACP) and The Research Council of Norway through project number 243953 ``Physical and Statistical Analysis of Climate Extremes in Large Datasets'' (ClimateXL). The source code for the analysis is implemented in the statistical programming language {\tt R} (\url{http://www.R-project.org}) and is available on GitHub at \url{http://github.com/eSACP/SeaLevelDecisions}.
\end{acknowledgments}
